Dysregulation of Cerebral Hemoglobin Content in Malawian Children with Malaria

### 2021-05-18 figures.Rmd
switch supplement figures again

  dplyr::rename("Mean across resamples" = "mean", "Standard error" = "std_err") %>% 
  mutate_if(is.numeric, round, 2) %>% 
  as.data.frame() %>%

@@

**Table 2.** Evaluation of the logistic regression model across 1000 bootstrap resamples.

>>>>

  dplyr::rename("Mean" = "mean", "Standard error" = "std_err") %>% 
  mutate_if(is.numeric, round, 2) %>% 
  as.data.frame() %>%

@@

**Table 2.** Evaluation of the best logistic regression model select from 1000.
